Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-06 thesis.Rmd
la till, men fråga om dubbel study sample

There were a total of `r merged` patients in the trauma registry. After excluding the patients younger than 15 and/or were dead on arrival, there were `r excluded` patients left. Out of those, `r sample` patients had been reviewed for the presence of OFI. A total of `r sample - log_reg_countBE` patients were excluded for the BE classification group due to missing data, resulting in `r log_reg_countBE` patients for the final analysis. For the SBP group, missing data accounted for exclusion of `r sample - log_reg_countSBP` patients, leaving a sum of `r log_reg_countSBP` patients for the final analysis.

>>>>

## Participants
There were a total of `r merged` patients in the trauma registry. After excluding the patients younger than 15 and/or were dead on arrival, there were `r excluded` patients left. Out of those, `r sample` patients had been reviewed for the presence of OFI. A total of `r sample - log_reg_countBE` patients were excluded for the BE classification group due to missing data, resulting in `r log_reg_countBE` patients for the final analysis. For the SBP group, missing data accounted for exclusion of `r sample - log_reg_countSBP` patients, leaving a sum of `r log_reg_countSBP` patients for the final analysis.

## Descriptive data
The study demographic median age is ... and the most common gender is male, `r male`.

The variable with most missing data is ... which lack the data for ... patients.

### BE classification
For the outcome OFI, out of the `r sample` patients reviewed, `r ofi` patients had a positive OFI. Clinically, the

### SBP classification

Report other analyses done—eg analyses of subgroups and interactions,
and sensitivity analyses 
-->

Table 3 present the sample characteristics.

Table 4 present
